Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-16 paper/v2.0/sections/appendix_a.tex
Add new version of the paper

The derivation of the solutions for the time dependent Schrödinger equation with our system's Hamiltonian (Eq. \ref{eq_1}) is quite similar to that followed in Refs. \cite{husimi53,dini16}. We start with expanding the Hamiltonian for two-dimensional case
\begin{equation} \label{eq_a1}
  \hat{H}_e(t) = \frac{1}{2m_e}\left[
    \left[\hat{p}_x + eBy \right]^2 +
    \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
  \right].
\end{equation}
Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
${L_x}^{-1/2}\exp(\frac{ip_x x}{\hbar})$ where $p_x = 2\pi \hbar m/L_x~$ with $ m \in \mathbb{Z}$.
Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
\begin{equation} \label{eq_a2}
    \hat{H}_e(t) = \frac{1}{2m_e}\left[
      \left[{p}_x + eBy \right]^2 +
      \left[-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right]^2
    \right].
\end{equation}
Subsequenty we define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 = {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 = {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian
\begin{equation} \label{eq_a3}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
      \frac{1}{2m_e}\bigg[
      -\hbar^2 \pdv[2]{\tilde{y}} & +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
      & +
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \bigg],
  \end{aligned}
\end{equation}
where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
\begin{equation} \label{eq_a4}
    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
\end{equation}
can be presented by the following form
\begin{equation} \label{eq_a5}
    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
    \bigg) \vartheta(\tilde{y},t),
\end{equation}
where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
\begin{equation} \label{eq_a6}
    \bigg[
    \frac{m_e \omega_0^2}{2}\tilde{y}^2
    - {eE\tilde{y}}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}}
    - i \hbar \dv{t}
    \bigg]
    \vartheta(\tilde{y},t) = 0.
\end{equation}
If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
\begin{equation} \label{eq_a7}
     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    \bigg]
    \vartheta(\tilde{y},t).
\end{equation}
Thus, we can identify $S(t) \equiv eE\sin(\omega t)$ term as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
\begin{equation} \label{eq_a8}
  \begin{aligned}
    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    - \tilde{y}S(t)]
    \bigg]
    \vartheta(\tilde{y},t).
  \end{aligned}
\end{equation}

This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}. We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
\begin{equation} \label{eq_a9}
    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
\end{equation}
This leads to
\begin{equation} \label{eq_a10}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   &=
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
        & +
        \Big[
            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
        \Big]y' \\
        &
        +
        \Big[
            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
        \Big]
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Subsequenty, we can restrict $\zeta(t)$ function such that
\begin{equation} \label{eq_a11}
  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
\end{equation}
and that simply our previous expression as
\begin{equation} \label{eq_a12}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
        &
        - L(\zeta,\dot{\zeta},t)
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Here
\begin{equation} \label{eq_a13}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
\end{equation}
is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
\begin{equation} \label{eq_a14}
    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
\end{equation}
and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
\begin{equation} \label{eq_a15}
    i \hbar \pdv{t} \chi(y',t)  =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
    \bigg] \chi(y',t).
\end{equation}
This is the well-known Schrödinger equation of the quantum harmonic oscillator.
This allows us to identify the well known eigenfunctions \cite{griffiths18,shankar94}
\begin{equation} \label{eq_a16}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y),
\end{equation}
with eigenvalues
\begin{equation} \label{eq_a17}
  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
  ~\text{for}~
  n \in \mathbb{Z}^{+}_0.
\end{equation}
Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
Thus, we can identify the solutions for Eq.~(\ref{eq_a8}) as
\begin{equation} \label{eq_a18}
  \begin{aligned}
    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \epsilon_nt +
    m_e\dot{\zeta(t)}\big[\tilde{y}-\zeta(t)\big] \\
     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}
Since $\chi_n(x)$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of the solutions derived in Eq.~(\ref{eq_a18}).

Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we derive the solution for Eq.~(\ref{eq_a11}) as
\begin{equation} \label{eq_a19}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
\end{equation}
Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
\begin{equation} \label{eq_a20}
  \begin{aligned}
    \psi_{n,m}&(x,y,t) \\
    &=  \frac{1}{\sqrt{L_x}}
    \chi_n\left(y - y_0 - \zeta(t)\right)\\
    &\quad\times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_nt
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
    & \quad\quad+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}

>>>>

The derivation of the solutions for the time-dependent Schrödinger equation with our system's Hamiltonian (Eq. \ref{eq_1}) is quite similar to that followed in Refs. \cite{husimi53,dini16}. We start with expanding the Hamiltonian for two-dimensional case
\begin{equation} \label{eq_a1}
  \hat{H}_e(t) = \frac{1}{2m_e}\left[
    \left[\hat{p}_x + eBy \right]^2 +
    \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
  \right].
\end{equation}
Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
${L_x}^{-1/2}\exp(\frac{ip_x x}{\hbar})$ where $p_x = 2\pi \hbar m/L_x~$ with $ m \in \mathbb{Z}$.
Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
\begin{equation} \label{eq_a2}
    \hat{H}_e(t) = \frac{1}{2m_e}\left[
      \left[{p}_x + eBy \right]^2 +
      \left[-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right]^2
    \right].
\end{equation}
Subsequenty we define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 = {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 = {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian
\begin{equation} \label{eq_a3}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
      \frac{1}{2m_e}\bigg[
      -\hbar^2 \pdv[2]{\tilde{y}} & +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
      & +
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \bigg],
  \end{aligned}
\end{equation}
where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
\begin{equation} \label{eq_a4}
    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
\end{equation}
can be presented by the following form
\begin{equation} \label{eq_a5}
    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
    \bigg) \vartheta(\tilde{y},t),
\end{equation}
where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
\begin{equation} \label{eq_a6}
    \bigg[
    \frac{m_e \omega_0^2}{2}\tilde{y}^2
    - {eE\tilde{y}}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}}
    - i \hbar \dv{t}
    \bigg]
    \vartheta(\tilde{y},t) = 0.
\end{equation}
If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
\begin{equation} \label{eq_a7}
     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    \bigg]
    \vartheta(\tilde{y},t).
\end{equation}
Thus, we can identify $S(t) \equiv eE\sin(\omega t)$ term as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
\begin{equation} \label{eq_a8}
  \begin{aligned}
    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    - \tilde{y}S(t)]
    \bigg]
    \vartheta(\tilde{y},t).
  \end{aligned}
\end{equation}

This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}. We introduce a time-dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
\begin{equation} \label{eq_a9}
    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
\end{equation}
This leads to
\begin{equation} \label{eq_a10}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   &=
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
        & +
        \Big[
            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
        \Big]y' \\
        &
        +
        \Big[
            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
        \Big]
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Subsequenty, we can restrict $\zeta(t)$ function such that
\begin{equation} \label{eq_a11}
  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
\end{equation}
and that simply our previous expression as
\begin{equation} \label{eq_a12}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
        &
        - L(\zeta,\dot{\zeta},t)
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Here
\begin{equation} \label{eq_a13}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
\end{equation}
is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
\begin{equation} \label{eq_a14}
    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
\end{equation}
and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
\begin{equation} \label{eq_a15}
    i \hbar \pdv{t} \chi(y',t)  =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
    \bigg] \chi(y',t).
\end{equation}
This is the well-known Schrödinger equation of the quantum harmonic oscillator.
This allows us to identify the well known eigenfunctions \cite{griffiths18,shankar94}
\begin{equation} \label{eq_a16}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y),
\end{equation}
with eigenvalues
\begin{equation} \label{eq_a17}
  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
  ~\text{for}~
  n \in \mathbb{Z}^{+}_0.
\end{equation}
Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
Thus, we can identify the solutions for Eq.~(\ref{eq_a8}) as
\begin{equation} \label{eq_a18}
  \begin{aligned}
    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \epsilon_nt +
    m_e\dot{\zeta(t)}\big[\tilde{y}-\zeta(t)\big] \\
     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}
Since $\chi_n(x)$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of the solutions derived in Eq.~(\ref{eq_a18}).

Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we derive the solution for Eq.~(\ref{eq_a11}) as
\begin{equation} \label{eq_a19}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
\end{equation}
Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time-dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
\begin{equation} \label{eq_a20}
  \begin{aligned}
    \psi_{n,m}&(x,y,t) \\
    &=  \frac{1}{\sqrt{L_x}}
    \chi_n\left(y - y_0 - \zeta(t)\right)\\
    &\quad\times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_nt
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
    & \quad\quad+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}

### 2021-08-16 paper/v2.0/sections/appendix_b.tex
Add new version of the paper

First we define the time integral of the Lagrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a period $T=2\pi/\omega$ as
\begin{equation} \label{eq_b1}
  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T dt' \; L(\zeta,\dot{\zeta},t').
\end{equation}
Additionally, performing this integral, we can obtain a more simplified result
\begin{equation} \label{eq_b2}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)}.
\end{equation}
Next, we define another parameter
\begin{equation} \label{eq_b3}
  \xi =
  \int_0^t dt' \; L(\zeta,\dot{\zeta},t') -
  \Delta_{\varepsilon} t,
\end{equation}
and after simplifying, we can identify
\begin{equation} \label{eq_b4}
  \xi =
  \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t),
\end{equation}
which is a periodic function in time. Using these parameters, we can factorize the wave function given in Eq.~(\ref{eq_2}) as linearly time dependent part and periodic time dependent part as follows
\begin{equation} \label{eq_b5}
  \begin{aligned}
    \psi_{\alpha}&(x,y,t)  =
    \exp(\frac{i}{\hbar}\qty[-\epsilon_nt + \Delta_{\varepsilon} t ])
    \frac{1}{\sqrt{L_x}} \chi_n\big(y - y_0 - \zeta(t)\big)
    \\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eEy}{\omega}\cos(\omega t) \\
     & \quad+
     m_e\dot{\zeta(t)}\big[y-\zeta(t)\big]
     + \int_0^{t}dt'L(\zeta,\dot{\zeta},t') - \Delta_{\varepsilon} t  \bigg]
     \bigg).
  \end{aligned}
\end{equation}
This leads to separate the linear time dependent phase component as the quasienergies
\begin{equation} \label{eq_b6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
while rest of the components as time-periodic Floquet modes
\begin{equation} \label{eq_b7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) =  &
    \frac{1}{\sqrt{L_x}} \chi_{n}\left(y - y_0 - \zeta(t)\right)
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x \\
     & +
     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg).
  \end{aligned}
\end{equation}

>>>>

First we define the time integral of the Lagrangian of the classical oscillator given in Eq.~(\ref{eq_5}), over a period $T=2\pi/\omega$ as
\begin{equation} \label{eq_b1}
  \Delta_{\varepsilon} = \frac{1}{T} \int_0^T dt' \; L(\zeta,\dot{\zeta},t').
\end{equation}
Additionally, performing this integral, we can obtain a more simplified result
\begin{equation} \label{eq_b2}
  \Delta_{\varepsilon} = \frac{(eE)^2}{4m_e(\omega_0^2 - \omega^2)}.
\end{equation}
Next, we define another parameter
\begin{equation} \label{eq_b3}
  \xi =
  \int_0^t dt' \; L(\zeta,\dot{\zeta},t') -
  \Delta_{\varepsilon} t,
\end{equation}
and after simplifying, we can identify
\begin{equation} \label{eq_b4}
  \xi =
  \frac{(eE)^2\qty(3\omega^2 - \omega_0^2)}{8m_e\omega(\omega_0^2 - \omega^2)^2} \sin(2\omega t),
\end{equation}
which is a periodic function in time. Using these parameters, we can factorize the wave function given in Eq.~(\ref{eq_2}) as linearly time-dependent part and periodic time-dependent part as follows
\begin{equation} \label{eq_b5}
  \begin{aligned}
    \psi_{\alpha}&(x,y,t)  =
    \exp(\frac{i}{\hbar}\qty[-\epsilon_nt + \Delta_{\varepsilon} t ])
    \frac{1}{\sqrt{L_x}} \chi_n\big(y - y_0 - \zeta(t)\big)
    \\
    & \times
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x +
     \frac{eEy}{\omega}\cos(\omega t) \\
     & \quad+
     m_e\dot{\zeta(t)}\big[y-\zeta(t)\big]
     + \int_0^{t}dt'L(\zeta,\dot{\zeta},t') - \Delta_{\varepsilon} t  \bigg]
     \bigg).
  \end{aligned}
\end{equation}
This leads to separate the linear time-dependent phase component as the quasienergies
\begin{equation} \label{eq_b6}
  \varepsilon_{n} =
  \hbar \omega_0\qty(n + \frac{1}{2}) - \Delta_{\varepsilon},
\end{equation}
while rest of the components as time-periodic Floquet modes
\begin{equation} \label{eq_b7}
  \begin{aligned}
    \phi_{n,m}(x,y,t) =  &
    \frac{1}{\sqrt{L_x}} \chi_{n}\left(y - y_0 - \zeta(t)\right)
    \text{exp}\bigg(
     \frac{i}{\hbar}\bigg[
     p_x x \\
     & +
     \frac{eE[y - y_0]}{\omega}\cos(\omega t) \\
     & +
     m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]
     + \xi \bigg]\bigg).
  \end{aligned}
\end{equation}
